Syntactic realization with data-driven neural tree grammars

### 2016-10-10 paper/draft.tex
commiting to merge

The grammar induction of \ref{sec:tree} allows us to constrcut an
inventory of supertags to match a corpus.  For NLG, we also need to
predict how likely a supertag is to fit a specific lexical item in the
context of a generation task.  We approach this problem using neural
networks. 
%
In particuaar, this work makes two contributions to improve stochastic
tree modeling with neural networks.
%
First, we represent supertags as vectors through embedding techniques
that enable to model to generalize naturally over complex, but related
structures.
%
Second, we address the hierarchical dependence between choices using a
recurrent tree network that can capture long-distance influences as
well as local ones.
%
We now describe these representations in more detail.

@@

Different supertags for the same word can encode differences in the
item's own combinatory syntax, differences in argument structure, and
differences in word order.  Accordingly, words have many related
supertags, with substantial overlaps in structure, and, presumably,
corresponding similarities in their patterns of occurrence.  A
traditional machine learning approach to supertag prediction would
treat individual supertags as atoms for classification; geenralizing
across supertags would require linking model parameters to handcrafted
features or backoff categories.

@@

\begin{align}
&\omega_{lex} = FC_1([G_w(lex_p); G_w(lex_c)]) \label{eq:fergusn} \\
&\omega_{node}=concat([G_\Lambda(tag_c);~\omega_{lex}]) \nonumber \\
&\Omega_{treelet} = concat([repeat(\omega_{node}),~G_\Lambda(tagset_p)]) \nonumber \\
&\Omega_{leaf} = concat([repeat(\omega_{lex}),~G_\Lambda(tagset_c)]) \nonumber \\
&P_\theta(tag_{p,i} | lex_{p}, lex_{c}, tag_{c})=
\frac{exp(\Psi(\omega_{treelet_i})))}
{\sum_{j \in |tagset_p|} exp(\Psi(\omega_{treelet_j})))} \nonumber \\
&P_\theta(tag_{c,i} |lex_{p}, lex_{c}) = 
\frac{exp(\Psi(\omega_{leaf_i})))}
{\sum_{j \in |tagset_c|} exp(\Psi(\omega_{leaf_j})))} \nonumber 
\end{align}

@@

\begin{table}
\centering
\begin{tabular}{|l|p{2cm}|c|c|c|}
\cline{3-4}
\multicolumn{2}{}{}& \multicolumn{2}{ |c| }{ \textbf{Accuracy}}&\multicolumn{1}{}{} \\ \hline
\textbf{Model} & \textbf{Embedding}  & \textbf{Before A*} 
& \textbf{After A*} & Running Time \\ \hline
Fergus-N &  Convolution &  58.17\% & 57.40\%  & 1.97s \\ \cline{2-5}
         &  Token       &  60.69\% & 55.56\% & 1.81s \\ \cline{2-5}
         & Minimal Token & 52.09\% & 54.18\% & 2.02s \\ \cline{2-5}
\hline
Fergus-R &  Convolution &  67.62\% & 57.04\% & 0.30s \\ \cline{2-5}
         &  Token       &  82.65\% & 62.73\% & 0.36s\\ \cline{2-5}
         &  Minimal Token & 10.13\% & 19.66\% & 0.54s \\ \cline{2-5}
\hline
\end{tabular}
\caption{For each supertag and embedding pair, the mean accuracy of supertag classification before and after the A* algorithm is shown. Also shown is the median running time---which includes model computation and A* search.}
\label{table:accresults}
\end{table}

@@

@@

>>>>

The grammar induction of \ref{sec:tree} allows us to constrcut an
inventory of supertags to match a corpus.  For NLG, we also need to
predict how likely a supertag is to fit a specific lexical item in the
context of a generation task.  We approach this problem using neural
networks. 
%
In particular, this work makes two contributions to improve stochastic
tree modeling with neural networks.
%
First, we represent supertags as vectors through embedding techniques
that enable to model to generalize naturally over complex, but related
structures.
%
Second, we address the hierarchical dependence between choices using a
recurrent tree network that can capture long-distance influences as
well as local ones.
%
We now describe these representations in more detail.

@@

Different supertags for the same word can encode differences in the
item's own combinatory syntax, differences in argument structure, and
differences in word order.  Accordingly, words have many related
supertags, with substantial overlaps in structure, and, presumably,
corresponding similarities in their patterns of occurrence.  A
traditional machine learning approach to supertag prediction would
treat individual supertags as atoms for classification; generalizing
across supertags would require linking model parameters to handcrafted
features or backoff categories.

@@

\begin{align}
&\omega_{lex} = FC_1([G_w(lex_p); G_w(lex_c)]) \label{eq:fergusn} \\
&\omega_{node}=concat([G_\Lambda(tag_c);~\omega_{lex}]) \nonumber \\
&\Omega_{treelet} = concat([repeat(\omega_{node}),~G_\Lambda(tagset_p)]) \nonumber \\
&\Omega_{leaf} = concat([repeat(\omega_{lex}),~G_\Lambda(tagset_c)]) \nonumber \\
&P_\theta(tag_{p,i} | lex_{p}, lex_{c}, tag_{c})=
\frac{exp(\Psi_{predict}(\omega_{treelet_i})))}
{\sum_{j \in |tagset_p|} exp(\Psi_{predict}(\omega_{treelet_j})))} \nonumber \\
&P_\theta(tag_{c,i} |lex_{p}, lex_{c}) = 
\frac{exp(\Psi_{predict}(\omega_{leaf_i})))}
{\sum_{j \in |tagset_c|} exp(\Psi_{predict}(\omega_{leaf_j})))} \nonumber 
\end{align}

@@

\begin{table}
\centering
\begin{tabular}{|l|p{3cm}|c|c|c|}
\cline{3-4}
\multicolumn{2}{}{}& \multicolumn{2}{ |c| }{ \textbf{Accuracy}}&\multicolumn{1}{}{} \\ \hline
\textbf{Model} & \textbf{Embedding}  & \textbf{Before A*} 
& \textbf{After A*} & Running Time \\ \hline
Fergus-N &  Convolution &  58.17\% & 57.40\%  & 1.97s \\ \cline{2-5}
         &  Token       &  60.69\% & 55.56\% & 1.81s \\ \cline{2-5}
         & Minimal Token & 52.09\% & 54.18\% & 2.02s \\ \cline{2-5}
\hline
Fergus-R &  Convolution &  67.62\% & 57.04\% & 0.30s \\ \cline{2-5}
         &  Token       &  82.65\% & 62.73\% & 0.36s\\ \cline{2-5}
         &  Minimal Token & 10.13\% & 19.66\% & 0.54s \\ \cline{2-5}
\hline
\end{tabular}
\caption{For each supertag and embedding pair, the mean accuracy of supertag classification before and after the A* algorithm is shown. Also shown is the median running time---which includes model computation and A* search.}
\label{table:accresults}
\end{table}

@@

In this appendix, we describe some design decisions that took place which did not have a place in the paper but should still be reported.  In particular, this section covers the data processing, parameters used in the final model, and design decisions for the restricting the supertag distributions.

@@

\subsection{Model design}

To facilitate efficient model computation, we restricted the computation for supertag distributions and used vectorized functions.
%
The set of supertags that are retrieved for probability distribution computation are set of supertags that are seen paired with the lexical item, reducing the output distribution from over 5000 to under 500.  
%
This was implemented as a set of indices to the embedding matrix passed into the computation with the rest of the data. 
%
Future implementations will explore having the supertag subset lookup table be part of the computation.
%
While there are several ways the affinity between supertag and lexical state vector could have been computed, we chose to concatenate the vectors, map them to a new space using a fully connected layer, and compute a score with a vectorized function.
%
The vectorized function operation is the same mechanism which calculates the probability distribution used in soft attention.
